Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-21 EconGrowth.Rnw
The cobbDouglas curve fits are now implemented as a function.

<<Load Data>>=
#################################
# This function loads data given a country name.
#
# countryName = the name of the country for which data is to be loaded. The file names is assumed to be 
#   named <countryName>Data.txt. The file is assumed to exist in a subfolder of this project called "data".
#
# returns a matrix with the data that has been loaded
##
loadData <- function(countryName){
  # Read the data file as a table with a header.  
  fileName <- paste("data/", countryName, "Data.txt", sep="")
  dataTable <- read.table(fileName, header = TRUE)
  # Identifies the header names associated with dataTable
  names(dataTable)
  return(dataTable)
}
@

@@

  # Checks validity of the model. AIC stands for Akaike's Information Criterion.
  aicCD  <- AIC(modelCD, k=2); aicCD

  summaryCD <- summary(modelCD) # Gives the nls summary table.
  print(summaryCD)
  ciCD <- confint(modelCD, level = 0.95); ciCD # Displays confidence intervals for the CD model.

@@

  coef(modelCD)

  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
  row.names(estCD) <- "Cobb-Douglas"
  #row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
  # The [1] subscripts pick off the lower confidence interval
  lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
  row.names(lowerCD) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
  row.names(upperCD) <- "+ 95% CI"

  # Now create the data for a table.
  dataCD <- rbind(upperCD, estCD, lowerCD); dataCD
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  return(tableCD)
}

tableCD <- cobbDouglas("US")

countries <- c("US", "CN")
tablesCD <- apply(countries, 1, cobbDouglas)
@

>>>>

<<Load Data>>=
#################################
# This function loads data given a country name.
#
# countryName = a string of the 2-digit code for the country for which data is to be loaded. 
#   The file name from which data will be loaded is assumed to be of the form 
#   "<countryName>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
#
# returns a matrix with the data that has been loaded
##
loadData <- function(countryName){
  # Read the data file as a table with a header.  
  fileName <- paste("data/", countryName, "Data.txt", sep="")
  dataTable <- read.table(fileName, header = TRUE)
  # Identifies the header names associated with dataTable
  print(names(dataTable))
  return(dataTable)
}
@

@@

  # Checks validity of the model. AIC stands for Akaike's Information Criterion.
  aicCD  <- AIC(modelCD, k=2)
  #print(aicCD)

  summaryCD <- summary(modelCD) # Gives the nls summary table.
  #print(summaryCD)
  ciCD <- confint(modelCD, level = 0.95); ciCD # Displays confidence intervals for the CD model.

@@

  #print(coef(modelCD))

  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
  #print(estCD)
  row.names(estCD) <- "Cobb-Douglas"
  #row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
  # The [1] subscripts pick off the lower confidence interval
  lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
  row.names(lowerCD) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
  row.names(upperCD) <- "+ 95% CI"

  # Now create the data for a table.
  dataCD <- rbind(upperCD, estCD, lowerCD)
  #print(dataCD)
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)
}

tableCD <- cobbDouglas("US")
print(tableCD)

countries <- c("US", "CN")
tablesCD <- lapply(countries, cobbDouglas)
#tablesCD <- sapply(countries, cobbDouglas, USE.NAMES = TRUE)
@
